Wissenschaftliches Arbeiten

### 2014-06-29 paper.tex
Replacing tupel brackets with a better version of them

First we want to formalize the setup: Following the notation of \cite[chapter~2]{BH01} a seller or an auction house wants to auction a set of $n$ indivisible goods $G = {g_1, ..., g_n}$. Every interested or authorized bidder can offer bids of the form $<b, p>$ where $b$ represents the bundle configuration and $p$ the price they are willing to pay.

When the offer phase is completed the seller has a set of all bids $B = {<b_i,p_i>}$. From this set they choose that subset of them which maximizes profit and is satisfiable. In essence satisfiability means that the same good cannot be sold more than once. Profit maximization computes for each satisfiable allocation $L \subset B$ the total value $v(L) = \sum \{p_i : <b_i,p_i> \subset L\}$ and chooses the maximum.\footnote{As explained in the first section there may be other objectives beside or instead of profit maximization in the auction but in commercial auctions the auctioneer's revenue is the main goal. So we will not provide further details for these expansions.}

@@

\cite{Nis00} calls this smallest possible bid of AND-connected items an ``atomic bid'' and also adds that if someone is willing to pay a price $p$ for a set $S$ of items they must also be willing to pay at least $p$ for any set $T$ with $S \subseteq T$. To be equivalent to the naive form these atomic bid must also be OR-conjunctional so that a bidder can submit several bundles he or she wants to bid for. Such bids can look like the fooling example: $\{<\{a\},1>,<\{b\},2>,<\{a,b\},4>\}$

@@

The implementation with both XOR and OR combinations still causes issues if one wants to construct bigger than usual bids. To ease the representation \cite{FLBS99} introduces dummy items which makes the use of XOR obsolete. The idea is that any XOR bid $<S_1,p_1> XOR <S_2, p_2>$ can be converted to the form $<S_1 \cup \{d_1\}, p_1> OR <S_2 \cup \{d_1\}, p_2>$ where $d_1$ is such a dummy object. Of course all dummy items of one bidder must be separated from the other bidders to prevent manipulation.

>>>>

First we want to formalize the setup: Following the notation of \cite[chapter~2]{BH01} a seller or an auction house wants to auction a set of $n$ indivisible goods $G = {g_1, ..., g_n}$. Every interested or authorized bidder can offer bids of the form $\langle b, p \rangle$ where $b$ represents the bundle configuration and $p$ the price they are willing to pay.

When the offer phase is completed the seller has a set of all bids $B = \{\langle b_i, p_i \rangle\}$. From this set they choose that subset of them which maximizes profit and is satisfiable. In essence satisfiability means that the same good cannot be sold more than once. Profit maximization computes for each satisfiable allocation $L \subset B$ the total value $v(L) = \sum \{p_i : \langle b_i, p_i \rangle  \subset L\}$ and chooses the maximum.\footnote{As explained in the first section there may be other objectives beside or instead of profit maximization in the auction but in commercial auctions the auctioneer's revenue is the main goal. So we will not provide further details for these expansions.}

@@

\cite{Nis00} calls this smallest possible bid of AND-connected items an ``atomic bid'' and also adds that if someone is willing to pay a price $p$ for a set $S$ of items they must also be willing to pay at least $p$ for any set $T$ with $S \subseteq T$. To be equivalent to the naive form these atomic bid must also be OR-conjunctional so that a bidder can submit several bundles he or she wants to bid for. Such bids can look like the fooling example: $\{ \langle \{a\}, 1 \rangle, \langle \{b\}, 2 \rangle, \langle \{a,b\},4 \rangle \}$

@@

The implementation with both XOR and OR combinations still causes issues if one wants to construct bigger than usual bids. To ease the representation \cite{FLBS99} introduces dummy items which makes the use of XOR obsolete. The idea is that any XOR bid $\langle S_1, p_1 \rangle \ XOR \ \langle S_2, p_2 \rangle $ can be converted to the form $\langle S_1 \cup \{d_1\}, p_1 \rangle \ OR \ \langle S_2 \cup \{d_1\}, p_2 \rangle $ where $d_1$ is such a dummy object. Of course all dummy items of one bidder must be separated from the other bidders to prevent manipulation.
